---
title: "Classwork 1_Samanta"
author: "Aritra Samanta"
date: "1/13/2022"
output: word_document
---
```{r}
library(tidyverse)
library(nycflights13)
library(lubridate)  # new package
library(dplyr)
```

1) Use and show R code to extract the month from the following datetime 
designation;
datetime2 <- ymd_hms("2021-11-13 10:05:31")
datetime2

```{r}
datetime2 <- ymd_hms("2021-11-13 10:05:31")
datetime2
month(datetime2, label=TRUE)
```
2) Use and show R code to extract the day of the week from the following 
datetime designation;
datetime2 <- ymd_hms("2021-11-13 10:05:31")
datetime2

```{r}
datetime2 <- ymd_hms("2021-11-13 10:05:31")
datetime2

wday(datetime2,label=TRUE)
```
3) Use and show R code to change the month to 8, and the hour to 5 for the 
following datetime designation
datetime2 <- ymd_hms("2021-11-13 10:05:31")
datetime2

```{r}
datetime2 <- ymd_hms("2021-11-13 10:05:31")
datetime2

update(datetime2, month=8, hour=5)
```
4) Use and show R code to change 6 hours to seconds. 
```{r}
dhours(6)
```
5) Use and show R code to change 4 days to seconds.
```{r}
ddays(4)
```
6) Use and show R code to add 7years to 30 days.
```{r}
years(7)+days(30)
```
7) Use and show R code to determine how many weeks there are from today's 
date to a year from now.
```{r}
next_year=today()+years(1)
next_year
(today() %--% next_year)%/%weeks(1)
```
8) Use and show R code to determine how many days there are between today's 
date and June 28, 2022.
```{r}
(today() %--% ("2022-06-28"))%/%days(1)
```

