---
title: "Classwork 2_Samanta"
author: "Aritra Samanta"
date: "1/19/2022"
output: word_document
---

```{r}
library(tidyverse)
```
1) In three or four sentences, explain why constructing a Function . in order to execute tasks, is beneficial or advantageous

Constructing a function is beneficial as it saves us from writing repeated lines of code which are susceptible to errors and unnecessary effort. We are also able to use functions to break down complex formulas into simpler parts that are more readable and accessible. Functions are also advantageous as they can be used for any value of the input you define it for (i.e. a formula for the volume of a cylinder will work for all integers); rather than simply coding the formula multiple times for different values. 

2) Write a function (using r code and structure demonstrated in class) to calculate a z score for a given observed value, a mean, and a standard deviation value. And then use your function to find a z score for the following problem. (Research the internet to find the formula used to calculate a z score)
Observed value = 25.77,  mean =  23.54,  standard deviation = 2.442
```{r}
Z<- function(X,M,S)
{z<-((X-M)/S)
  print(paste("the result is",z))}
Z(25.77,23.54,2.442)


```
3) Write a function (using r code and the structure demonstrated in class) to calculate the natural log of a number multiplied by the common log of the same number divided by the cube root of a given prime number.
Use your function to find the answer if the number to be used for both log expressions is 32 and the given prime number is 11.
Also use R code to round your answer to the nearest tenth
```{r}
#rounding in the function
Log<-function(x,y)
{l=(log(x)*log10(x))/y**(1/3)
  print(paste("The natural log of", x, "multiplied by the common log of",x,"divided by a prime number",y, "is", round(l, digits=1)))}
Log(32,11)

```
4)Use and show R coding to calculate the standard deviation for each variable of the data table mtcars using the “Special For Loop Method” demonstrated in the class notes.
```{r}
 mtcars 
 
mtsd <- vector("double", ncol(mtcars))   
 for (i in seq_along(mtcars)) {              
   mtsd[[i]] <-sd(mtcars[[i]])         
 }
 mtsd
 
```


