---
title: "Homework 3"
author: "Aritra Samanta"
date: "1/27/2022"
output: word_document
---
```{r}
library(tidyverse)
library(dplyr)
library(purrr)
```

```{r}
Vector1 <- (c( 10, 19, 121, 83, 63, 7, 77, 61, 51, 97, 123, 41))
```




1)  For the vector given above, use and show two methods of R coding to extract the first 
element and the last element.
```{r}
Vector1[c(1,12)]
q1=Vector1[Vector1==10 | Vector1==41]
q1
```

2)  For the vector given above, use and show two methods of R coding to extract all of the 
elements that are less than 60.
```{r}
Vector1[Vector1<60]
Vector1[c(1,2,6,9,12)]
```

3)  For the vector given above, use and show two methods of R coding to extract all numbers 
that are not divisible by 2 or 3.
```{r}
Vector1[Vector1 %% 2 != 0 & Vector1 %% 3 != 0]
Vector1[c(2,3,4,6,7,8,10,12)]


```
4)  Use and show two R coding methods to confirm that Vector1 does not have missing values
```{r}
myList <-  list(TRUE, 12.35, 'pear', 48, c = 3:8, list(23, 'team'))
myList 

str(myList[!is.na(myList)])
str(myList[]) #clearly there are no NA's here or else it would have reported as logi NA!
```
 5) For the list given above, use and show R coding to confirm that “pear” is a character 
element.
```{r}
str(myList[3])
```
6) For the list given above, use and show R coding to extract the first three elements of the list.
```{r}
str(myList[1:3])
```

7) Use the $ operator to extract the element “pear” from your list. Be sure to use and show 
required R code to produce the requested output.
```{r}
myList <-  list(TRUE, 12.35, p='pear', 48, c = 3:8, list(23, 'team')) #creating a new variable p for pear so the $ can extract it

myList$p
```

8) Use and show R code to write a function to solve the following quadratic equations by using 
the quadratic formula.  (all equations have two real number solutions)
a)  x2- 3x - 28 = 0                                                                                                                                              
b)  x2 + x  - 30 = 0                                                                                                                                           
c) 3x2+ 14x + 8 = 0                                                                                                                                        
d) 2x2+11x = 6
```{r}
quadratic <- function(a,b,c){
  { x_1 = (-b+sqrt(delta(a,b,c)))/(2*a)
    x_2 = (-b-sqrt(delta(a,b,c)))/(2*a)
    result = c(x_1,x_2)
  }
  }
# Constructing delta
delta<-function(a,b,c){
      b^2-4*a*c
} #from: https://rpubs.com/kikihatzistavrou/80124

a=quadratic(1,-3,-28)
a
b=quadratic(1,1,-30)
b
c=quadratic(3,14,8)
c
d=quadratic(2,11,-6)
d
```

9) In your book (towards the end of chapter 16) a special set of vectors are defined as 
Augmented Vectors.  One such augmented vector is a Tibble. Use and show R code that will 
produce the Tibble shown below.  Do not simply type or copy and paste. You must show and 
use R coding that will output the tibble.
```{r}
z= rev(seq(0.5,5,by=0.5))
t=tibble::tibble(x = 1:10, y = 10:1, z=z)
t

```
10) In statistics, the Interquartile Range is the difference between Q3 and Q1.  Now show and 
use map function coding to find the Interquartile Range for each column of the tibble from 
number 9.
```{r}
map_dbl(t, IQR)
```












